\documentclass{shivam_resume} % Use the custom shivam_resume.cls style
\usepackage[left=0.4 in,top=0.2in,right=0.4in,bottom=0.2in]{geometry} % Document margins
\usepackage{fontawesome5}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{SHIVAM KAG}

\address{
\href{mailto:shivamkag32@gmail.com}{\faEnvelope\ {shivamkag32@gmail.com}} \\
\href{tel:+919399217512}{\faPhone\ {+919399217512}} \\
\href{https://www.linkedin.com/in/shivam-kag-a86508250/}{\faLinkedin\ {shivam-kag}}
}

\begin{document}

%---------------------------------------------------------
% EDUCATION
%---------------------------------------------------------
\begin{rSection}{EDUCATION}
 {\bf Bachelor of Technology in Computer Science and Engineering} \hfill {Nov 2021 -- July 2025}\\
    \textit{Swami Vivekanand College of Engineering, Indore, India \hfill {7.67 CGPA}}
\vspace{0.2em}

 {\bf XII Standard} \hfill {2021}\\
    \textit{Nirmal Vidhyapeeth Barwaha. School \hfill {60\%}}
\vspace{0.2em}

 {\bf X Standard} \hfill {2019}\\
    \textit{Nirmal Vidhyapeeth Barwaha School \hfill {60\%}}
\vspace{-0.4em}
\end{rSection}

%---------------------------------------------------------
% SKILLS
%---------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}
\textbf{Programming Languages:} C, C++, JavaScript, Dart \newline
\textbf{Frontend Tech:} HTML, CSS, React.Js, Flutter \newline
\textbf{Developer Tools / Version Control:} VS Code, Git, Github, FlutterFlow, Supabase, Firebase \newline
\textbf{Course Fundamentals:} Data Structure and Algorithm, OOPS
\end{rSection}

%---------------------------------------------------------
% EXPERIENCE
%---------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Software Developer — \href{https://narma.dev/}{Narma Devs}} \hfill {June 2025 -- Present}
\vspace{0.5em}

\textbf{Swell Breaks App} \hfill \href{https://swell-breaks.flutterflow.app/}{\faLink\ Live App} \\
\textit{FlutterFlow, Supabase}
\begin{itemize}
\itemsep -3pt
\small
\item Designed and developed a mobile application using FlutterFlow, focusing on rapid development and responsive UI.
\item Implemented interactive layouts and customized components to deliver a seamless user experience across devices.
\item Integrated Supabase for secure user authentication and utilized its APIs for efficient data storage and management.
\end{itemize}

\textbf{WhatFBO App} \hfill \href{https://play.google.com/store/apps/details?id=uk.co.creatanet.whatfbo}{\faGooglePlay\ Play Store} \\
\textit{FlutterFlow, OpenAI, Supabase}
\begin{itemize}
\itemsep -3pt
\small
\item Built and published a mobile application to the Google Play Store using FlutterFlow for cross-platform deployment.
\item Integrated OpenAI API to power an intelligent in-app chat feature, enabling interactive AI-driven conversations.
\item Utilized Supabase for robust backend data management and secure user authentication across the app.
\end{itemize}

\textbf{Gotogether App} \\
\textit{FlutterFlow, Supabase, Firebase, Paystack}
\begin{itemize}
\itemsep -3pt
\small
\item Developed a comprehensive carpooling application featuring distinct user roles for drivers and passengers to seamlessly post and find rides.
\item Integrated Paystack payment gateway to facilitate secure and seamless in-app transactions for ride bookings.
\item Implemented real-time in-app notifications using Firebase to enhance user communication and engagement.
\item Built a dedicated administrative panel to monitor application activity, manage users, and oversee ride operations.
\item Utilized Supabase for robust backend data management and secure user authentication.
\end{itemize}

\end{rSection}

%---------------------------------------------------------
% PROJECTS
%---------------------------------------------------------
\begin{rSection}{PROJECTS}

\textbf{Gemini AI Chatbot Clone} \hfill \href{https://github.com/Shivam-Kag/Gemini-Clone}{\faGithub\ GitHub} \\
\textit{HTML, CSS, JavaScript, React.Js}
\begin{itemize}
\itemsep -3pt
\small
\item Developed interactive, dynamic, and reusable components using React.js to build modern web applications.
\item Utilized React hooks like useState and useEffect for efficient state management and to handle side effects during API interactions.
\item Integrated with a conversational AI API to process user input and display real-time responses, mimicking human-like conversations.
\end{itemize}

\end{rSection}

%---------------------------------------------------------
% CERTIFICATIONS
%---------------------------------------------------------
\begin{rSection}{CERTIFICATIONS}
\begin{itemize}
\itemsep -4pt
\small
\item Winner Of College Hackathon
\item Data Structures and Algorithms using C++
\end{itemize}
\end{rSection}

\end{document}
